---
title: "Student Sit In"
author: "Glen Abram"
date: "10/28/2019"
output: 
  html_document:
    toc: true
    number_sectons: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ONE SHOT assignment!
this is an extra credit assignment, must be completed Monday Oct 28, turn-in closes at midnight!

## Problem statement: 
Students at UCD- is there a relation between where one sits and one's major? 

## Introduction  

<!-- where is the data found?  Is this an experiment or an observational study?  !-->

Data from this study came from a study at UC DAVIS among 173 students.



```{r include=FALSE, echo=FALSE}
library(tigerstats)
data(ucdavis1)

```

$H_0$: there is no relationship between one's major and where one sits in a class   
$H_A$: where one sits in class and one's major are related  

<!-- Get the data: !-->

names of the data in the data frame

```{r echo=FALSE}
UCDdataframe = data.frame(seat=ucdavis1$Seat, major=ucdavis1$class, data=ucdavis1)
names(UCDdataframe)
```
## Methods

Both variables in this analysis are categorical, therefore we utilize bar graphs and tables to manifest the data and char squared test for inference.


## Data summary

**Graphical summary**

```{r}
barchartGC(~seat+major, data = UCDdataframe, type = "percent", xlab = "Seating", main = "Seating vs Major")

```

The BarChart shows that amongst people whom Majored in Liberal Arts. They are approximately evenly divided on whether they favor front or not. People who are non liberal arts majors tend to be in favor of of the middle.

**Numerical summary**
put numerical summary here

```{r}
tab1 = xtabs(formula = ~seat+major, data = UCDdataframe)
rowPerc(tab1)
```

There's not much difference among seating preferences amongst majors.

## Inferential Results
put the inferential test for the the null hypothesis here

```{r}
chisqtestGC(tab1)
```

what is the p-value?0.2173>0.05 suggests that there's no connection among where one chooses to sit and their major.

## Results and conclusions

<!-- explain-- is there evidence that certain majors tend to sit in particular areas of the class?  Can the results of this test be generalized to all majors in all universities? !-->

The P value for the ChisQ Test is 0.2173>0.05 therefore, we fail to reject the null hypothesis and conclude that we have sufficient evidence to corroborate the contention that one's major and where one chooses to sit is related. It appears very likely that one's choice of seating is not related to one's choice of major.

<!--
push results to your github account, turn in the URL

--OR--

If you did not fork my repo to your github account,
create a repository in your github account for this project, get the URL for that repo and 
(in the terminal window..)

$git remote add origin URL_of_your_github_repo
$git push -u origin master

!-->